---
title: 'FIN580: Midterm'
author: "Chris, Utsav, Srishti"
date: "Spring 2020"
output:
  html_document:
    df_print: paged
    toc: no
    toc_depth: 4
  word_document:
    toc: no
    toc_depth: '4'
  pdf_document:
    fig_caption: yes
    toc: no
    toc_depth: 4
geometry: margin=1.5in
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align="center", fig.height=5.5, fig.width=6, collapse=TRUE, comment="", prompt=TRUE, echo = TRUE, cache=TRUE, autodep=TRUE, cache.comments=FALSE)
options(width=63)
```

--------

# Objective

To forecast daily volatilities of major stock indexes after the COVID-19 outbreak and provide risk measures than can help portfolio managers to make investment decisions during this turbulent period.

--------

# Data Preparation

I use the following libraries and set my working directory.
```{r eval = F}
library('fasttime')
library('data.table')
library('dplyr')
library('matrixStats')
library('bit64')
library('ggplot2')
library('gdata')
library('naniar')
library('mice')
library('forecast')
library('imputeTS')
setwd("/Users/srishtisingla/Downloads")
```


```{r eval = F}
data = read.xls('data.xlsx')  
summary(data)
```

```{r eval = F}
#transforming data to get value for each security as a column
grid <- as.data.frame(as.character(unique(data$X)))
names(grid) <- "X"
symbols <- as.character(unique(data$Symbol))
for (i in 1:length(symbols)){
  mergewith <- data[as.character(data$Symbol)==symbols[i],-c(2)]
  names(mergewith) <- c("X",paste0("open",symbols[i]),paste0("close",symbols[i]),paste0("rv",symbols[i]))
  grid <- merge(grid,mergewith, by=c("X"), all = TRUE )
}
# grid has 5303 rows, and 94 columns

sample <- grid[2625:5303,]
# 2679 rows to get data starting from 2010 (we need to choose this carefully)
```

```{r eval = F}
col <- c(1, seq(from=2, to=92, by = 3))
vis_miss(sample[,col]) # total 6.7% missing data, most for BVLG and STI
gg_miss_var(sample[,col])
```

```{r fig.width=10, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("missingdata.png")
 grid.raster(img)
```

```{r fig.width=5, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("missingcount.png")
 grid.raster(img)
```

## Different ways of dealing with missing data

**Linear interpolation**

```{r eval = F}
linear_imputed_data <- na_interpolation(sample, option = "linear") 
```

**Spline interpolation**

```{r eval = F}
spline_imputed_data <- na_interpolation(sample, option = "spline") 
```

To visualize what's happening-

Want to see what happens in case of an index like AORD

```{r eval = F}
plotNA.imputations(sample$open.AORD[1:300], linear_imputed_data$open.AORD[1:300])
```

```{r fig.width=3.5, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("AORDlinear.png")
 grid.raster(img)
```

```{r eval = F}
plotNA.imputations(sample$open.AORD[1:300], spline_imputed_data$open.AORD[1:300])
```

```{r fig.width=3.5, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("AORDspline.png")
 grid.raster(img)
```

For STI which has a lot of missing data in the beginning itself what do the two models do-

(The linear method basically fills one value for them all whereas spline does not)

```{r eval = F}
plotNA.imputations(sample$open.STI[1000:1800], linear_imputed_data$open.STI[1000:1800])
```

```{r fig.width=3.5, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("STIlinear.png")
 grid.raster(img)
```

```{r eval = F}
plotNA.imputations(sample$open.STI[1000:1800], spline_imputed_data$open.STI[1000:1800])
```

```{r fig.width=3.5, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("STIspline.png")
 grid.raster(img)
```


